A large-scale analysis of racial disparities in police stops across the United

### 2019-07-30 lib/paper_results.Rmd
Adjust bounds for threshold paper plot

```{r veil_of_darkness-main_mod}
vod$dst %>% 
  filter(spline_degree == 6, agency_control, interact_time_loc) %>% 
  kable()
```

@@

```{r disparity-city-thresholds-plot, fig.height=5, fig.width=10}
disp$city$threshold$plots$aggregate + 
  theme(legend.position = "none", plot.title = element_blank()) + 
  scale_x_continuous(
    limits = c(axis_min, axis_max),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

>>>>

```{r veil_of_darkness-main_mod}
vod$dst %>% 
  filter(spline_degree == 6, agency_control, !interact_time_loc) %>% 
  kable()
```

@@

```{r disparity-city-thresholds-plot, fig.height=5, fig.width=10}
axis_min <- max(
  min(
    disp$city$threshold$plots$aggregate$data$minority_rate,
    disp$city$threshold$plots$aggregate$data$majority_rate
  ) - 0.05, 0
)
axis_max <- min(
  max(
    disp$city$threshold$plots$aggregate$data$minority_rate,
    disp$city$threshold$plots$aggregate$data$majority_rate
  ) + 0.05, 1
)
disp$city$threshold$plots$aggregate + 
  theme(legend.position = "none", plot.title = element_blank()) + 
  scale_x_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```
